Differnces-in-Differences with Spatial Spillover

### 2020-11-19 latex/slides/Spillover_slides.tex
Renamed slides to Spillover_slides

\imageframe{../../figures/figure-bias_from_prob_treat.png}

@@

\imageframe{../../figures/figure-bias_fix.png}

@@

\imageframe{../../figures/figure-krig.png}

@@

\imageframe{../../figures/figure-bias_from_spatial_autocorr.png}

\imageframe{../../figures/figure-bias_fix_spatial_autocorr.png}

>>>>

\imageframe{../../figures/figure-bias_from_prob_treat_slides.png}

@@

\imageframe{../../figures/figure-bias_fix_slides.png}

@@

\imageframe{../../figures/figure-krig_slides.png}

@@

\imageframe{../../figures/figure-bias_from_spatial_autocorr_slides.png}

\imageframe{../../figures/figure-bias_fix_spatial_autocorr_slides.png}
